Application for Rethinking Foundations of Physics 2017

### 2017-01-14 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Proposed Question} Only focus on one question..

--- next section

@@

>>>>

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. This raises an important philosophical question with
immense practical relevance in the context of quantum computing. The
question, which we could largely bypass in the classical case, is
whether there is, in the background of all the measurements and probabilities,
a ``real'' infinitely-precise quantum state that is being approximated
and that, in principle, can be more and more accurately described
given more and more resources.

@@

\subsection{Quantum Bayesianism}

Although we discussed how a quantum IVPM could be induced from a real
quantum state, our investigation leaves an open question of whether
there exists a ``real'' entity that exists independently of measurements
and probabilities. Since the frequency interpretation of probability
is problematic, it is much more sensible to interpret probability
in the Bayesian sense as ``lack of knowledge''. This, and similar
arguments elegantly expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
suggest that the quantum state is more like an interactive system
in computer science parlance. In other words, the state is only determined
by its interactions with the environment or observers. A rough but
useful analogy in the context of computer science would be a web server:
the state of such a system cannot be said to exist independently of
the interactions with clients; each interaction with a client determines
a future state of the system and may affect future interactions. Crucially,
each client may have a \emph{different} view of the web server that
is consistent with their own history of interactions. This computational
perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
that asserts that the quantum state is subjective: each observer has
a different view of the quantum system that is consistent with their
previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.

\section{Kick-off Talk: The Reality of the Quantum State}

— next section
